### 2025-01-26 my_paper/manuscript_main.tex
submit to JODE

In this section, I explore the empirical relationship between bias and interracial marriages, as well as the migration patterns of second-generation Asian immigrants as robustness checks to my main analysis and the effect of proxy response on my results. I examine the impact of biases on the likelihood of interracial marriages, focusing on interracial couples, and the migration decisions of Asian individuals within the United States.

@@

I present the results of estimating equation (\ref{eq:inter-interracial}) in Table (\ref{regtab-logit-02}). I find that a one standard deviation increase in bias increases the probability of having interracial parents by 4 percentage points. Moreover, I break down the analysis by the ethnicity of the couples. A one standard deviation increase in bias is associated with 1 percentage points decrease in the chances of a Asian husband marrying a White wife. A one standard deviation increase in bias is associated a 3 percentage points increase in the chances of a Asian wife having a White husband. The fact that bias and interracial marriage are positively correlated could be a result of the fact that Asian immigrants in states with high bias might aim to decrease the likelihood that their children will display Asian ethnicity signals. For example, Asian women in high bias states might marry a non-Asian White husband, so their children will have a non-Asian last name.\footnote{I show the results of estimating the relationship between bias and interracial marriages as a logistic regression in Table (\ref{regtab-logit-03}).}

>>>>

In this section, I explore the empirical relationship between bias and interracial marriages. I also analyze migration patterns of second-generation Asian immigrants and the effect of proxy response on my results as robustness checks to my main analysis. I examine the impact of biases on the likelihood of interracial marriages, focusing on interracial couples, and the migration decisions of Asian individuals within the United States.

@@

I present the results of estimating equation (\ref{eq:inter-interracial}) in Table (\ref{regtab-logit-02}). I find that a one standard deviation increase in bias increases the probability of having interracial parents by 4 percentage points. Moreover, I break down the analysis by the ethnicity of the couples. A one standard deviation increase in bias is associated with 1 percentage points decrease in the chances of a Asian husband marrying a White wife. A one standard deviation increase in bias is associated a 3 percentage points increase in the chances of a Asian wife having a White husband. The fact that bias and interracial marriage are positively correlated could be a result of the fact that Asian immigrants in states with high bias might aim to decrease the likelihood that their children will display Asian ethnicity signals. For example, Asian women in high bias states might marry a non-Asian White husband, so their children will have a non-Asian last name.\footnote{I show the results of estimating the relationship between bias and interracial marriages as a logistic regression in Table (\ref{regtab-logit-03}).} This positive correlation between bias and interracial marriage provides a robustness check on my main results, as it suggests an additional mechanism through which bias affects identity choices beyond direct self-reporting decisions.

### 2025-01-26 output/tables/tab47-marriage.tex
submit to JODE

\begin{table}[H]
\centering\centering
\caption{Logistic Regression Analysis of Bias and Interracial Marriages \label{regtab-logit-03}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{1}{c}{Asian Men} & \multicolumn{1}{c}{Asian Women} \\
\cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4}
  & \specialcell{(1) \\ Interethnic} & \specialcell{(2) \\ Interethnic} & \specialcell{(3) \\ Interethnic}\\
\midrule
Bias & $0.38$*** & $-0.19$ & $0.33$**\\
 & ($0.11$) & ($0.16$) & ($0.14$)\\
College Graduate: Wife & $0.35$*** & $0.44$*** & $0.56$***\\
 & ($0.04$) & ($0.06$) & \vphantom{1} ($0.05$)\\
College Graduate: Husband & $-0.06$ & $-0.03$ & $-0.15$***\\
 & ($0.04$) & ($0.06$) & ($0.05$)\\
\midrule
Observations & $69,800$ & $52,032$ & $60,171$\\
Year $\times$ Region FE & X & X & X\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{This is the result to estimating (\ref{eq:inter-interethnic}) as a
                        logistic regression. The coefficients are exponentiated, thus should be interpreted as odds ratios.}
\item[2] \footnotesize{I include controls for partners' sex, age, education, 
                      and years since immigrating to the United States.
                      Standard errors are clustered on the household level.}
\item[3] \footnotesize{Data source is the 2004-2020 Current Population Survey Data.}
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Logistic Regression Analysis of Bias and Interracial Marriages \label{regtab-logit-03}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{1}{c}{Asian Men} & \multicolumn{1}{c}{Asian Women} \\
\cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4}
  & \specialcell{(1) \\ Interracial} & \specialcell{(2) \\ Interracial} & \specialcell{(3) \\ Interracial}\\
\midrule
Bias & $1.47$*** & $0.83$ & $1.39$**\\
 & ($0.16$) & ($0.14$) & ($0.20$)\\
College Graduate: Wife & $1.42$*** & $1.55$*** & $1.75$***\\
 & ($0.06$) & ($0.09$) & ($0.09$)\\
College Graduate: Husband & $0.94$ & $0.97$ & $0.86$***\\
 & ($0.04$) & ($0.06$) & ($0.04$)\\
\midrule
Observations & $69,800$ & $52,032$ & $60,171$\\
Year $\times$ Region FE & X & X & X\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{This is the result to estimating (\ref{eq:inter-interracial}) as a
                        logistic regression. The coefficients are exponentiated, thus should be interpreted as odds ratios.}
\item[2] \footnotesize{I include controls for partners' sex, age, education, 
                      and years since immigrating to the United States.
                      Standard errors are clustered on the household level.}
\item[3] \footnotesize{Data source is the 2004-2020 Current Population Survey Data.}
\end{tablenotes}
\end{threeparttable}
\end{table}
